LEGWORK: A python package for computing the evolution and detectability \\ of stellar-origin gravitational-wave sources with space-based detectors

### 2021-11-16 src/ms.tex
some final acknowledgements

\begin{acknowledgements}
    % People
    We are grateful to Stas Babak, Floor Broekgaarden, Tom Callister, Will Farr, Stephen Justham, Valeria Korol, Mike Lau, Tyson Littenberg, Ilya Mandel, Alberto Sesana, Lieke van Son, the CCA GW group, the BinCosmos group and the COMPAS group for stimulating discussions that influenced and motivated us to complete this project. We thank the BinCosmos group for testing an early version of the package and providing useful feedback. In particular, we thank Lieke van Son for her innovation in inventing the name \lw{}! TW also thanks Floor Broekgaarden for first suggesting that he investigate LISA and the derivation of the SNR calculation.

>>>>

\begin{acknowledgements}
    % People
    We are grateful to Stas Babak, Floor Broekgaarden, Tom Callister, Will Farr, Stephen Justham, Valeria Korol, Mike Lau, Tyson Littenberg, Ilya Mandel, Alberto Sesana, Lieke van Son, the CCA GW group, the BinCosmos group and the COMPAS group for stimulating discussions that influenced and motivated us to complete this project. We thank the BinCosmos group for testing an early version of the package and providing useful feedback. In particular, we thank Lieke van Son for her innovation in inventing the name \lw{}!  TW thanks Floor Broekgaarden for first suggesting that he investigate LISA and the derivation of the SNR calculation. KB thanks Shane L. Larson and Kyle Kremer for \emph{several} conversations about the SNR derivation.
